---
title: "mfrmr Linking and DFF"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{mfrmr Linking and DFF}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 7,
  fig.height = 5
)
```

This vignette covers the package-native route for:

- checking whether a design is connected enough for a common scale
- exporting anchor candidates from an existing fit
- screening differential facet functioning (DFF)
- deciding when subgroup contrasts are descriptive versus formally comparable

For a broader workflow guide, see `vignette("mfrmr-workflow", package = "mfrmr")`.
For the shorter help-page map, see
`help("mfrmr_linking_and_dff", package = "mfrmr")`.

## Minimal setup

```{r setup}
library(mfrmr)

bias_df <- load_mfrmr_data("example_bias")

fit <- fit_mfrm(
  bias_df,
  person = "Person",
  facets = c("Rater", "Criterion"),
  score = "Score",
  method = "MML",
  model = "RSM",
  quad_points = 7
)

diag <- diagnose_mfrm(fit, residual_pca = "none")
```

## 1. Check connectedness first

Use `subset_connectivity_report()` before interpreting subgroup or cross-form
contrasts.

```{r connectivity}
sc <- subset_connectivity_report(fit, diagnostics = diag)

sc$summary[, c("Subset", "Observations", "ObservationPercent")]
plot(sc, type = "design_matrix", preset = "publication")
```

Interpretation:

- Sparse rows or columns indicate weaker design coverage.
- Weak coverage should lower confidence in subgroup comparisons.

## 2. Export anchor candidates

`make_anchor_table()` is the shortest route when you need reusable anchor
elements from an existing calibration.

```{r anchors}
anchors <- make_anchor_table(fit, facets = "Criterion")
head(anchors)
```

Use `audit_mfrm_anchors()` when you want a stricter review of anchor quality.

## 3. Residual DFF as a screening layer

Residual DFF is the fast screening route. It is useful for triage, but it is
not automatically a logit-scale inferential contrast.

```{r dff-residual}
dff_resid <- analyze_dff(
  fit,
  diag,
  facet = "Criterion",
  group = "Group",
  data = bias_df,
  method = "residual"
)

dff_resid$summary
head(
  dff_resid$dif_table[, c("Level", "Group1", "Group2", "Classification", "ClassificationSystem")],
  8
)
plot_dif_heatmap(dff_resid)
```

Interpretation:

- Treat `residual` output as screening evidence.
- Check `ClassificationSystem` to see how the current residual screen was labeled.
- Reserve `ScaleLinkStatus` and `ContrastComparable` for refit-based contrasts.

## 4. Refit DFF when subgroup comparisons are defensible

The refit route can support logit-scale contrasts only when subgroup linking is
adequate and the precision layer supports it.

```{r dff-refit}
dff_refit <- analyze_dff(
  fit,
  diag,
  facet = "Criterion",
  group = "Group",
  data = bias_df,
  method = "refit"
)

dff_refit$summary
head(
  dff_refit$dif_table[, c("Level", "Group1", "Group2", "Classification", "ContrastComparable")],
  8
)
```

## 5. Cell-level follow-up

If the level-wise screen points to a specific facet, follow up with the
interaction table and narrative report.

```{r dff-follow-up}
dit <- dif_interaction_table(
  fit,
  diag,
  facet = "Criterion",
  group = "Group",
  data = bias_df
)

head(dit$table)

dr <- dif_report(dff_resid)
cat(dr$narrative)
```

## 6. Multi-wave anchor review

When you work across administrations, the route usually moves from anchor
export to anchored fitting and then to drift review.

```{r drift-route, eval = FALSE}
d1 <- load_mfrmr_data("study1")
d2 <- load_mfrmr_data("study2")

fit1 <- fit_mfrm(d1, "Person", c("Rater", "Criterion"), "Score",
                 method = "JML", maxit = 25)
fit2 <- fit_mfrm(d2, "Person", c("Rater", "Criterion"), "Score",
                 method = "JML", maxit = 25)

anchored <- anchor_to_baseline(
  d2,
  fit1,
  person = "Person",
  facets = c("Rater", "Criterion"),
  score = "Score"
)

drift <- detect_anchor_drift(list(Wave1 = fit1, Wave2 = fit2))
plot_anchor_drift(drift, type = "drift", preset = "publication")
```

## Recommended sequence

For a compact linking route:

1. `fit_mfrm()`
2. `diagnose_mfrm()`
3. `subset_connectivity_report()`
4. `make_anchor_table()` or `audit_mfrm_anchors()`
5. `analyze_dff()`
6. `dif_report()` and `plot_dif_heatmap()`
7. `anchor_to_baseline()` / `detect_anchor_drift()` when working across waves

## Related help

- `help("mfrmr_linking_and_dff", package = "mfrmr")`
- `help("subset_connectivity_report", package = "mfrmr")`
- `help("analyze_dff", package = "mfrmr")`
- `help("detect_anchor_drift", package = "mfrmr")`
