---
title: "mfrmr Workflow"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{mfrmr Workflow}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 7,
  fig.height = 5
)
```

This vignette outlines a reproducible workflow for:

- loading packaged simulation data
- fitting an MFRM with flexible facets
- running diagnostics and residual PCA
- generating APA and visual summary outputs

## Load Data

```{r load-data}
library(mfrmr)

list_mfrmr_data()

data("ej2021_study1", package = "mfrmr")
head(ej2021_study1)

study1_alt <- load_mfrmr_data("study1")
identical(names(ej2021_study1), names(study1_alt))
```

## Minimal Runnable Example

We start with a small toy dataset that fits quickly:

```{r toy-setup}
toy <- expand.grid(
  Person = paste0("P", 1:4),
  Rater = paste0("R", 1:2),
  Criterion = c("Content", "Organization", "Language"),
  stringsAsFactors = FALSE
)
toy$Score <- (
  as.integer(factor(toy$Person)) +
  2 * as.integer(factor(toy$Rater)) +
  as.integer(factor(toy$Criterion))
) %% 3

fit_toy <- fit_mfrm(
  data = toy,
  person = "Person",
  facets = c("Rater", "Criterion"),
  score = "Score",
  method = "JML",
  model = "RSM",
  maxit = 15
)
diag_toy <- diagnose_mfrm(fit_toy, residual_pca = "none")

summary(fit_toy)$overview
summary(diag_toy)$overview
names(plot(fit_toy, draw = FALSE))
```

## Diagnostics and Reporting

```{r diagnostics-reporting}
t4_toy <- unexpected_response_table(
  fit_toy,
  diagnostics = diag_toy,
  abs_z_min = 1.5,
  prob_max = 0.4,
  top_n = 10
)
t12_toy <- fair_average_table(fit_toy, diagnostics = diag_toy)
t13_toy <- bias_interaction_report(
  estimate_bias(fit_toy, diag_toy,
                facet_a = "Rater", facet_b = "Criterion",
                max_iter = 2),
  top_n = 10
)

class(summary(t4_toy))
class(summary(t12_toy))
class(summary(t13_toy))

names(plot(t4_toy, draw = FALSE))
names(plot(t12_toy, draw = FALSE))
names(plot(t13_toy, draw = FALSE))
```

## Fit and Diagnose with Full Data

For a realistic analysis, we use the packaged Study 1 dataset:

```{r fit-full}
fit <- fit_mfrm(
  data = ej2021_study1,
  person = "Person",
  facets = c("Rater", "Criterion"),
  score = "Score",
  method = "MML",
  model = "RSM"
)

diag <- diagnose_mfrm(
  fit,
  residual_pca = "both",
  pca_max_factors = 6
)

summary(fit)
summary(diag)
```

## Residual PCA and Reporting

```{r residual-pca}
pca <- analyze_residual_pca(diag, mode = "both")
plot_residual_pca(pca, mode = "overall", plot_type = "scree")
```

```{r bias-apa}
bias <- estimate_bias(fit, diag, facet_a = "Rater", facet_b = "Criterion")
fixed <- build_fixed_reports(bias)
apa <- build_apa_outputs(fit, diag, bias_results = bias)

mfrm_threshold_profiles()
vis <- build_visual_summaries(fit, diag, threshold_profile = "standard")
vis$warning_map$residual_pca_overall
```

## Human-Readable Reporting API

```{r reporting-api}
spec <- specifications_report(fit, title = "Study run")
data_qc <- data_quality_report(
  fit,
  data = ej2021_study1,
  person = "Person",
  facets = c("Rater", "Criterion"),
  score = "Score"
)
iter <- estimation_iteration_report(fit, max_iter = 8)
subset_rep <- subset_connectivity_report(fit, diagnostics = diag)
facet_stats <- facet_statistics_report(fit, diagnostics = diag)
cat_structure <- category_structure_report(fit, diagnostics = diag)
cat_curves <- category_curves_report(fit, theta_points = 101)
bias_rep <- bias_interaction_report(bias, top_n = 20)
plot_bias_interaction(bias_rep, plot = "scatter")
```
